Forecasting the United States 2024 Presidential Election Using State as Fixed Effect Through a Bayesain Approach

### 2024-11-04 paper/paper.qmd
typo

- **Support**  
  *Definition:* The support level for candidate \( i \) in a given poll.  
  *Justification:* Measures the proportion of respondents supporting candidate \( i \), providing insight into their current standing.

- **Sample Size**  
  *Definition:* Represents the number of respondents in poll \( i \).  
  *Justification:* Larger sample sizes generally yield more accurate estimates of support, reducing sampling variability.

- **Days to election**  
  *Definition:* Denotes the number of days remaining until the election when poll \( i \) was conducted.  
  *Justification:* Accounts for temporal proximity to the election, capturing potential fluctuations in support as the election approaches.

@@

where \(N_s\) is the number of polls for state \(s\).

>>>>

- **Support**  
  *Definition:* The support level for candidate in a given poll.  
  *Justification:* Measures the proportion of respondents supporting candidate, providing insight into their current standing.

- **Sample Size**  
  *Definition:* Represents the number of respondents in poll.  
  *Justification:* Larger sample sizes generally yield more accurate estimates of support, reducing sampling variability.

- **Days to election**  
  *Definition:* Denotes the number of days remaining until the election when poll was conducted.  
  *Justification:* Accounts for temporal proximity to the election, capturing potential fluctuations in support as the election approaches.

@@

where \(N\) is the number of polls for state.
